### 2019-01-05 Sections/economics_of_the_quantum_internet.tex
+quotes, formatting

@@

>>>>

\famousquote{If you put the federal government in charge of the Sahara Desert, in 5 years there'd be a shortage of sand.}{Milton Friedman}
\newline

\famousquote{It is not from the benevolence of the butcher, the brewer, or the baker that we expect our dinner, but from their regard to their own interest.}{Adam Smith}
\newline

@@

\famousquote{In a dream it's typical not to be rational.}{John Nash}
\newline

### 2019-01-05 Sections/essay_security_implications_of_the_global_quantum_internet.tex
+quotes, formatting

@@

Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\famousquote{I don't even know why any of us are here. This is the worst job I've ever had.}{John Kelly}}.

>>>>

\famousquote{I don't even know why any of us are here. This is the worst job I've ever had.}{John Kelly}
\newline

@@

Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}.

### 2019-01-05 Sections/essay_the_quantum_mind.tex
Crypto section update
Blockchain complete
Essays reformat
+quotes, formatting

\subsection{The quantum mind}\index{Quantum mind}

\comment{To do: quantum machine learning and AI. QCs improve training process.}

>>>>

\section{The quantum mind}\index{Quantum mind}\label{sec:quantum_mind}

\sectionby{Nana Liu}

\famousquote{If computers get too powerful, we can organise them into committees. That'll do them in.}{Unknown}
\newline

\comment{To do: quantum machine learning and AI. QCs improve training process. Implications of strong AI for humanity.}

\comment{Selfishness arises naturally in evolution as a simple winning strategy in game theory. Need to make sure quantum AI doesn't become selfish. Must become collaborative/altruistic rather than selfish, so that it serves us rather than itself.}
